Plots for Latent Hawkes Paper

### 2021-07-11 output_scripts/Paper_Plots.Rmd
tidy up stan code, reformat prediction and diagnostics to account for cmdstan output, also correcting multiple places where the incorrect pair wise base rates were being used. this should make a difference to the results which will be interesting to see. corresponding updates to paperplots to use the revised output

load(paste(data_path, cohort_names[current_cohort],
  "/cohort_hp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f, 2, mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort,
  raw_df =
    full_data[[cohort_names[current_cohort]]],
  clean_data
)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

@@

load(paste(data_path, cohort_names[current_cohort],
  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)

@@

gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
eta1_mean <- mean(sim_cohort_dchp$eta_1)
eta2_mean <- mean(sim_cohort_dchp$eta_2)
eta3_mean <- mean(sim_cohort_dchp$eta_3)

@@

@@

for(current_cohort in 1:10) {
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  eta1_mean <- mean(sim_cohort_hp$eta_1)
  eta2_mean <- mean(sim_cohort_hp$eta_2)
  eta3_mean <- mean(sim_cohort_hp$eta_3)
  f_est <- apply(sim_cohort_hp$f, 2, mean)
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort,
    raw_df =
      full_data[[cohort_names[current_cohort]]],
    clean_data
  )
  unique_pairs_df <- return_df %>%
    group_by(initiator, recipient) %>%
    dplyr::summarize(
      count = n(),
      observe = list(observe.id),
      observe.length = list(observe.time),
      no.events = list(no.events)
    )
  unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

@@

  ### c-dchp
  gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
  zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)
  eta1_mean <- mean(sim_cohort_dchp$eta_1)
  eta2_mean <- mean(sim_cohort_dchp$eta_2)
  eta3_mean <- mean(sim_cohort_dchp$eta_3)

@@

@@

```{r new-fig-4a, eval = revision_plots}
sim_data_path <- here("output", "revisions", "sim_m3", "sim_3", "/")

@@

sims <- 1:20
sims <- sims[c(-9, -13)]

@@

true_ranks <- tibble(node = rep(1:num_nodes,3),
                     true_rank = rep(f_vec,3),
                     model = c(rep("C-HP", 10),rep("C-DCHP", 10),
                               rep("C-MMHP", 10)))
true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)

@@

### TO DO
### need to check this here for pairs with less than cut off events

for (i in seq_along(lam0_vec)) {
  row_id <- clean_sim_data$I_fit[i]
  col_id <- clean_sim_data$J_fit[i]
  lam0_par_est[row_id, col_id] <- lam0_vec[i]
  lam1_par_est[row_id, col_id] <- lam1_vec[i]
}

###

#############
mmhp_par_est <- list(
  lambda0 = lam0_par_est,
  lambda1 = lam1_par_est,
  eta_1 = mean(sim_model3_stan_sim3$eta_1),
  eta_2 = mean(sim_model3_stan_sim3$eta_2),
  eta_3 = mean(sim_model3_stan_sim3$eta_3),
  beta = mean(sim_model3_stan_sim3$beta),
  f = apply(f_draws, 2, mean)
)

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 3
## 2 and 8 maybe look better
## 3 probably looks the best

@@

>>>>

data_path <- "../output/revisions/"

load(paste(data_path, cohort_names[current_cohort],
  "/cohort_hp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))

eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)

f_draws <- sim_cohort_hp %>% select(starts_with("f"))

f_est <- apply(f_draws, 2, mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort,
  raw_df =
    full_data[[cohort_names[current_cohort]]],
  clean_data
)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

@@

load(paste(data_path, cohort_names[current_cohort],
  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))

gamma_draws <- sim_cohort_dchp %>% select(starts_with("gamma"))
zeta_draws <- sim_cohort_dchp %>% select(starts_with("zeta"))

gamma_mean <- apply(gamma_draws, 2, mean)
zeta_mean <- apply(zeta_draws, 2, mean)

@@

gamma_mean <- apply(gamma_draws, 2, mean)
zeta_mean <- apply(zeta_draws, 2, mean)
eta1_mean <- mean(sim_cohort_dchp$eta_1)
eta2_mean <- mean(sim_cohort_dchp$eta_2)
eta3_mean <- mean(sim_cohort_dchp$eta_3)

@@

What is `data_path` here?

@@

for(current_cohort in 1:10) {
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_hp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  load(paste(data_path, cohort_names[current_cohort],
    "/cohort_dchp_stan_result_", cohort_names[current_cohort],
    ".RData",
    sep = ""
  ))
  eta1_mean <- mean(sim_cohort_hp$eta_1)
  eta2_mean <- mean(sim_cohort_hp$eta_2)
  eta3_mean <- mean(sim_cohort_hp$eta_3)
  f_draws <- sim_cohort_hp %>% select(starts_with("f"))

  f_est <- apply(f_draws, 2, mean)
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort,
    raw_df =
      full_data[[cohort_names[current_cohort]]],
    clean_data
  )
  unique_pairs_df <- return_df %>%
    group_by(initiator, recipient) %>%
    dplyr::summarize(
      count = n(),
      observe = list(observe.id),
      observe.length = list(observe.time),
      no.events = list(no.events)
    )
  unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

@@

  ### c-dchp
  gamma_draws <- sim_cohort_dchp %>% select(starts_with("gamma"))
  zeta_draws <- sim_cohort_dchp %>% select(starts_with("zeta"))
  gamma_mean <- apply(gamma_draws, 2, mean)
  zeta_mean <- apply(zeta_draws, 2, mean)
  eta1_mean <- mean(sim_cohort_dchp$eta_1)
  eta2_mean <- mean(sim_cohort_dchp$eta_2)
  eta3_mean <- mean(sim_cohort_dchp$eta_3)

@@

Further diagnostic plots for C-HP vs C-DCHP

```{r plot-pvalues-m1-m2-here}
ks_p %>% filter(ks_p != 0) %>%
  select(-cols) %>% 
  mutate(id = row_number()) %>% 
  pivot_wider(names_from = method, values_from = ks_p)

bind_cols(M1_ks_p, M2_ks_p) %>% 
  rename(chp_p = ks_p...1, cdchp_p = ks_p...3) %>% 
  filter(chp_p != 0) %>% 
  ggplot(aes(chp_p, cdchp_p)) + geom_point() +
  labs(x = "C-HP p Value", y = "C-DCHP p Value",
       title = "p Value for C-HP and C-DCHP") +
  theme_minimal()

@@

```{r new-fig-4a, eval = revision_plots, message=FALSE, warning=FALSE}
sim_data_path <- here("output", "revisions", "sim_m3", "sim_2", "/")

@@

sims <- 1:50
sims <- sims[c(-18)]

@@

true_ranks <- tibble(node = rep(1:num_nodes,3),
                     true_rank = rep(f_vec,3),
                     model = c(rep("C-HP", 10), rep("C-DCHP", 10),
                               rep("C-MMHP", 10)))
true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)

@@

for (i in seq_along(lam0_vec)) {
  row_id <- clean_sim_data$I_fit[i]
  col_id <- clean_sim_data$J_fit[i]
  lam0_par_est[row_id, col_id] <- lam0_vec[i]
  lam1_par_est[row_id, col_id] <- lam1_vec[i]
}
###
#############
mmhp_par_est <- list(
  lambda0 = lam0_par_est,
  lambda1 = lam1_par_est,
  eta_1 = mean(sim_model3_stan_sim3$eta_1),
  eta_2 = mean(sim_model3_stan_sim3$eta_2),
  eta_3 = mean(sim_model3_stan_sim3$eta_3),
  beta = mean(sim_model3_stan_sim3$beta),
  f = apply(f_draws, 2, mean)
)

@@

```{r fig-7-prMatrix-Cohort3, fig.width=7, fig.height=7}
current_cohort <- 5
data_path <- "../output/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

```{r m1-m2-pr, fig.width=6}
current_cohort <- 5
m1_m2_plot <- list(m1_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ],
  m2_pr[
    rev(expert_rank_10[[current_cohort]]),
    expert_rank_10[[current_cohort]]
  ])

myMultiMatrixPlot(
  X = m1_m2_plot, no_matrix = 2, n_row = 1,
  xLabels = expert_rank_10[[current_cohort]],
  yLabels = rev(expert_rank_10[[current_cohort]]),
  min = -80, max = 80, axis_cex = 2, title_cex = 1.8,
  colorPalette = "RdBu", if.emp = FALSE,
  # legend.mar=c(0.5,.5,0.5,0.5),
  title_lst = list("C-HP", "C-DCHP"),
  # title_lst = list("I-MMHP"),
  col_axis = c(-80, -40, 0, 40, 80), fake_matrix = TRUE,
  matrix.mar = c(2.5, 2.5, 2.5, 1)
)
```
